### 2022-03-12 [2020-08]_ACMTOMS_(MQSI)/paper/mqsi20.tex
Added some missing red, moved location of visual files to be in the paper directory.

% Abstract and Introduction
{\rmVIII\parindent=0pt MQSI is a Fortran 2003 subroutine for constructing
monotone quintic spline interpolants to \red{univariate} monotone data. Using sharp
theoretical monotonicity constraints, first and second derivative estimates
at data provided by a quadratic facet model are refined to produce a
\red{univariate} $\scriptstyle C^2$ monotone interpolant.  Algorithm and implementation
details, complexity and sensitivity analyses, usage information, a
brief performance study, and comparisons with other spline approaches are included.

>>>>

% Abstract and Introduction
{\rmVIII\parindent=0pt MQSI is a Fortran 2003 subroutine for constructing
monotone quintic spline interpolants to \red{univariate} monotone data. Using sharp
theoretical monotonicity constraints, first and second derivative estimates
at data provided by a quadratic facet model are refined to produce a
\red{univariate} $\scriptstyle C^2$ monotone interpolant.  Algorithm and implementation
details, complexity and sensitivity analyses, usage information, a
brief performance study, \red{and comparisons with other spline approaches} are included.
